### 2016-05-19 2016-lrec-tyvmorph/poster.tex
moar hargling
git-svn-id: https://svn.code.sf.net/p/apertium/svn/branches/papers/@68635 72bbbca6-d526-0410-a7d9-f06f51895060

	\headerbox{What should we put here}{name=harglebargle,column=0,below=morphtrans}{
		\vspace{0.35in}

		\headerbox{Development cycle}{name=development,below=harglebargle,span=1}{
		\centering
		\begin{tikzpicture}[xscale=1.45,yscale=2.5]%, auto]

@@

		\headerbox{Further information}{name=getting,column=0,below=references,span=3}{
			\tikzoverlay[text height=1in] at (0in, 0.04in) {
				\includegraphics[angle=90,height=1in]{apertium5b}
			};
			%\tikzoverlay[text width=0.8in] at (6.2in, 0.04in) {
			\tikzoverlay[text height=1in] at (10in, 0.04in) {
				\includegraphics[height=1in]{qrcode}
			};
			\tikzoverlay[text height=0.5in] at (6.75in, 0in) {
				\parbox{3in}{
				\centering
				{\huge \textbf{Четтирдивис!}}\\
				\texttt{четтир\tag{v}\tag{tv}\tag{ifi}\tag{p1}\tag{pl}}\vspace{1em}\\
				{\Large \url{http://turkic.apertium.org/}}
				}
			};
			\tikzoverlay[text width=6in] at (1in, 0.04in) {
			\begin{itemize}
				\item Part of \textbf{Apertium Turkic} project:\ \url{http://wiki.apertium.org/wiki/Apertium\_Turkic}
				\item Transducers available \textbf{live} on our website: \url{http://turkic.apertium.org/} %\href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				\item \textbf{Source code} under \hiliteone{GPL} from Apertium's SVN repo
				%\item Transducers available \textbf{live} at \href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				%\item \textbf{Source code} of transducers available under \hiliteone{GPL} (free!) from Apertium's SVN repo
				%info at {\small \url{http://wiki.apertium.org/wiki/apertium-kir}}
				\item Multilingual Turkic RBMT \textbf{mailing list} (>25 subscribers):\ \texttt{apertium-turkic@lists.sourceforge.net}%\\
				%\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
				\item And feel free to contact the authors any time!
			\end{itemize}
			\vspace{0.3em}
			};
			\vspace{1in}
		}

>>>>

	\headerbox{What should we put here}{name=harglebargle,column=0,below=morphtrans}{
		\begin{tabular}{lllll}
		\toprule
			stem & V & C & dative & genitive \\
		\midrule
			медаль & а & ль & медальга & медальдың \\
			ансамбль & а & бль & ансамбльге & ансамбльдиң \\
			руль & у & ль & рульга & рульдуң \\
			рубль & у & бль & рубльге & рубльдиң \\
		\bottomrule
		\end{tabular}
\codeex{\hilitegrey{"\{I\} harmony"\\
	\%\{I\%\}:Vy <=> :Vx [ :Cns* :RealCns ]/[ :0 | \%- ]* \_ ;}\\
	\-~~~~~~~~~except\\
	\-~~~~~~~~~~~~~[ :BackVow :Cns* :Cns :л ь: :Cns* :RealCns ]/:0* \_ ;\\
	\-~~~~~~~~~~~~~[ :BackVow :Cns* :Cns :л ь:0 ]/:[ :0 - ь: ]* \_ ;\\
	\-~~~~~~~~~\hilitegrey{where Vx in ( ү и е э ө а о ы у я ё ю )\\
	\-~~~~~~~~~~~~~~ Vy in ( ү и и и ү ы у ы у ы у у )\\
	\-~~~~~~~~~matched ;}\\
	\\
	"\{I\} always front when intervening Cль"\\
	\%\{I\%\}:и <=> [ :BackVow :Cns* :Cns :л ь: :Cns* :RealCns ]/:0* \_ ;\\
	\-~~~~~~~~~~~~[ :BackVow :Cns* :Cns :л ь:0 ]/:[ :0 - ь: ]* \_ ;}
	}

		\headerbox{Development cycle}{name=development,below=harglebargle,span=1}{
		\centering
		\begin{tikzpicture}[xscale=1.45,yscale=2.2]%, auto]

@@

		\headerbox{Further information}{name=getting,column=0,below=development,span=3}{
			\tikzoverlay[text height=1in] at (0in, 0.04in) {
				\includegraphics[angle=90,height=1in]{apertium5b}
			};
			%\tikzoverlay[text width=0.8in] at (6.2in, 0.04in) {
			\tikzoverlay[text height=1in] at (10in, 0.04in) {
				\includegraphics[height=1in]{qrcode}
			};
			\tikzoverlay[text height=0.5in] at (6.75in, 0in) {
				\parbox{3in}{
				\centering
				{\huge \textbf{Четтирдивис!}}\\
				\texttt{четтир\tag{v}\tag{tv}\tag{ifi}\tag{p1}\tag{pl}}\vspace{1em}\\
				{\Large \url{http://turkic.apertium.org/}}
				}
			};
			\tikzoverlay[text width=6in] at (1in, 0.04in) {
			\begin{itemize}
				\item Part of \textbf{Apertium Turkic} project:\ \url{http://wiki.apertium.org/wiki/Apertium\_Turkic}
				\item Transducers available \textbf{live} on our website: \url{http://turkic.apertium.org/} %\href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				\item \textbf{Source code} under \hiliteone{GPL} from Apertium's SVN repo
				%\item Transducers available \textbf{live} at \href{http://turkic.apertium.org/}{\texttt{turkic.apertium.org}}
				%\item \textbf{Source code} of transducers available under \hiliteone{GPL} (free!) from Apertium's SVN repo
				%info at {\small \url{http://wiki.apertium.org/wiki/apertium-kir}}
				\item Multilingual Turkic RBMT \textbf{mailing list} (>25 subscribers):\ \texttt{apertium-turkic@lists.sourceforge.net}%\\
				%\vspace{-0.5ex}Feel free to post in any language!\\\vspace{-2.5ex}
				\item And feel free to contact the authors any time!
			\end{itemize}
			\vspace{0.3em}
			};
			\vspace{1in}
		}
